Designing Types for R, Empirically

### 2020-05-16 paper/main.tex
Added pipeline figure

For this paper, we have built tooling to (\emph{a}) automate the extraction
of raw type signatures from execution traces, (\emph{b}) infer type
signatures from a set of raw types, and (\emph{c}) validate the inferred
signatures by the means of contracts. This section presents each step
of this pipeline.

>>>>

For this paper, we have built tooling to (\emph{a}) automate the extraction of
raw type signatures from execution traces, (\emph{b}) infer type signatures from
a set of raw types, and (\emph{c}) validate the inferred signatures by the means
of contracts. This section presents each step of this pipeline (\emph{cf.}
Figure~\ref{fig:pipeline}). The pipeline is run in parallel using GNU
parallel~\cite{tange2011_parallel} on Intel Xeon 6140, 2.30GHz with 72 cores and
256GB of RAM).

\begin{figure}[t!]
  \vspace{2mm}
  \includegraphics[width=\textwidth]{plots/analysis-pipeline.pdf}
  \caption{The Analysis Pipeline. (1) the rather long time is because we had to
    extract metadata from all CRAN packages before we could compose our
    \PACKAGES package corpus.}
  \label{fig:pipeline}
\end{figure}
